Modern Graph Generators: A Survey

### 2018-09-12 generators_GraphDatabases.tex
Minor corrections

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks designed particularly for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590}. Or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark specific for graph databases if necessary.

Paper~\cite{Dominguez-Sal:2010:DDG:1946050.1946053} discusses this question and related topics. On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark.

In the following paragraphs we overview graph data generators and benchmarks primarily targeting graph DBMSs.

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services.

It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space. 
The workload generator of YCSB supports definition of new workload types. XGDBench involves basic operations read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.

The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes. 
The generated graphs are thus in MAG format, with power-law degree distribution thus closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties. A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented.

\paragraph{GraphGen}  GraphAware GraphGen~\cite{GraphGen} is a graph generation engine based on Cypher, Neo4j's\footnote{\url{https://neo4j.com/}} query language.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both 
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson and CypherQueries) or loaded directly to a DBMS. However, it is probably not maintained anymore.

\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain- and query language-independent graph instance and query workload generator.  It leverages a schema definition,
called a \emph{graph configuration}, which includes the enumeration of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data, along with their properties in generated instances (occurrence constraints, degree distribution, etc.). \emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.). The authors prove that given a graph configuration $G$, deciding whether there exists a graph satisfying $G$ is NP-complete. And, that given a query workload configuration $Q$, deciding
whether there exists a query workload satisfying $Q$ is NP-complete. Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time. gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher, SPARQL, SQL and LogicQL.

>>>>

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks designed particularly for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590}. Or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark specific for graph databases is necessary. \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics. On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark. In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space.
The workload generator of YCSB supports definition of new workload types. XGDBench involves basic operations read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties. A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.

\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent graph instance and query workload generator.  It leverages a schema definition,
called a \emph{graph configuration}, which includes the enumeration of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data, along with their properties in generated instances (occurrence constraints, degree distribution, etc.). \emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.). The authors prove that given a graph configuration $G$, deciding whether there exists a graph satisfying $G$ is NP-complete. And, that given a query workload configuration $Q$, deciding
whether there exists a query workload satisfying $Q$ is NP-complete. Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time. gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.

\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS. However, it is probably not maintained anymore.

### 2018-09-12 generators_SocialNetworks.tex
Minor corrections

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day and thus providing extremely
useful information for various domains. However, an analysis of such type of
graph has to cope with two problems: (1) availability of the data and (2)
privacy of the data. Hence, data generators which provide realistic synthetic
social network graphs are in great demand. In general, analyses of social networks identify their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the minimum number of hops in which some
fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
usually low due to weak ties joining faraway cliques. Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real graphs and output by existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
found among different graphs follow quite similar distributions and that
communities in a single graph have diverse nature, and are difficult to fit with
a single model.

Network generators can be categorized into statistical and agent-based.
\emph{Statistical
approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
focus on reproducing aspects of the network statistics. In \emph{agent-based
approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
the networks are constructed by directly simulating the agents' social choices.

@@

\paragraph{Towards More Realistic Data} ~\cite{Nettleton2016} argued that the main body of existing work lies in
topology generation which approximate the characteristics of a real social
network (such as a small graph diameter, small average path length, skew degree
distribution, and community structures), however without data. Hence, they
introduced a general stochastic modeling system which allows the users to
populate a graph topology with data. The approach has three steps: (1) topology
generation (using R-MAT) plus community identification using the Louvain
method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
(following distribution profiles, attribute value definitions, using a
parameterizable set of data propagation rules and affinities), and (3) data
population.

>>>>

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day and thus providing extremely
useful information for various domains. However, an analysis of such type of
graph has to cope with two problems: (1) availability of the data and (2)
privacy of the data. Hence, data generators which provide realistic synthetic
social network graphs are in a great demand.

In general, analyses of social networks identify their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the minimum number of hops in which some
fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
usually low due to weak ties joining faraway cliques.

Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real-world graphs and outputs of existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They discover that communities found in different graphs follow quite similar distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.

The existing social network generators try to reproduce different aspects of the
generated network. They can be categorized into statistical and agent-based.
\emph{Statistical
approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
focus on reproducing aspects of the network. In \emph{agent-based
approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
the networks are constructed by directly simulating the agents' social choices.

@@

\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the main body of existing work lies in
topology generation which approximate the characteristics of a real social
network (such as a small graph diameter, small average path length, skew degree
distribution, and community structures), however without data. Hence, they
introduced a general stochastic modeling system which allows the users to
populate a graph topology with data. The approach has three steps: (1) topology
generation (using R-MAT) plus community identification using the Louvain
method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
(following distribution profiles, attribute value definitions, using a
parameterizable set of data propagation rules and affinities), and (3) data
population.
